---
title: "Ireland COVID-19 modelling"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE,
                      message = FALSE)

library(deSolve)
library(doParallel)
library(doRNG)
library(dplyr)
library(GGally)
library(ggplot2)
library(ggpubr)
library(imputeTS)
library(lubridate)
library(pomp)
library(purrr)
library(readr)
library(readsdr)
library(readxl)
library(scales)
library(stringr)
library(tictoc)
library(tidyr)

source("./R_scripts/helpers.R")
source("./R_scripts/apple.R")
```


# Data

```{r}
source("./R_scripts/irish_data.R")

irish_data  <- get_irish_data()
total_cases <- sum(irish_data$y)
```


## Epicurve 

```{r, fig.height = 3}
formatted_tc <- format(total_cases, big.mark = ",")

 ggplot(irish_data, aes(x = date, y = y)) +
  geom_col(colour = "white", fill = "steelblue", alpha = 0.95) +
  theme_pubr() +
  geom_vline(xintercept = as_date("2020-02-29") + 13, colour = "grey50",
             linetype = "dotted") +
  geom_vline(xintercept = as_date("2020-02-29") + 28, colour = "grey10",
             linetype = "dotted") +
  annotate("text", x = as_date("2020-02-29") + 13.5, y = 750, 
           label = "Delay phase", hjust = 0, size = 3, colour = "grey50") +
  annotate("text", x = as_date("2020-02-29") + 28.5, y = 920, 
           label = "Stay at home", hjust = 0, size = 3, colour = "grey50") +
  labs(x = "Date of Lab specimen collection",
       y = "Incidence [new cases per day]",
       subtitle = str_glue("Total cases: {formatted_tc}")) +
  theme(axis.title.y = element_text(size = 8),
        plot.subtitle = element_text(size = 8, colour = "grey60"))
```

## Trend

```{r g_trend_incidence, fig.height = 3}
ggplot(irish_data, aes(x = date, y = y)) +
  geom_vline(xintercept = as_date("2020-02-29") + 13, colour = "grey50",
             linetype = "dotted") +
  geom_vline(xintercept = as_date("2020-02-29") + 28, colour = "grey10",
             linetype = "dotted") +
  annotate("text", x = as_date("2020-02-29") + 13.5, y = 750, 
           label = "Delay phase", hjust = 0, size = 3, colour = "grey50") +
  annotate("text", x = as_date("2020-02-29") + 28.5, y = 930, 
           label = "Stay at home", hjust = 0, size = 3, colour = "grey50") +
  labs(x = "Date of Lab specimen collection",
       y = "Incidence [new cases per day]") +
  geom_point(colour = "steelblue") +
  stat_smooth(se = FALSE, span = 0.25, colour = "lightskyblue3") +
  theme_pubclean()
```


# Model

## Process model

\begin{equation}
    \frac{dS}{dt} = - S(t) \lambda(t)
\end{equation}

\begin{equation}
   \frac{dE}{dt} = S(t) \lambda(t) - \sigma E(t)
\end{equation}

\begin{equation}
   \frac{dP}{dt} = \omega \sigma E(t) - \eta P(t)
\end{equation}

\begin{equation}
   \frac{dI}{dt} =  \eta P(t) - \gamma I(t)
\end{equation}

\begin{equation}
   \frac{dA}{dt} =  (1-\omega) \sigma E(t) - \kappa A(t)
\end{equation}

\begin{equation}
   \frac{dR}{dt} =  \kappa A(t) - \gamma I(t)
\end{equation}

\begin{equation}
   \lambda =  \frac{\beta(t) (I(t) + P(t) + \mu A(t))}{N(t)} 
\end{equation}

\begin{equation}
   \frac{d\beta}{dt} =  \alpha \beta(t) dW 
\end{equation}

\begin{equation}
   dW \sim Normal(0, \sqrt{dt})
\end{equation}

\begin{equation}
   \frac{dC}{dt} =  \rho \eta P(t)
\end{equation}

\begin{equation}
   x_1(t) =  C(t) - C(t-1)
\end{equation}

### Initial conditions

* $S(0) = 4999970 - P(0)$ [persons]

* $E(0) = 0$ [persons]

* $\boldsymbol{P(0) = ?}$ [persons]

* $I(0) = 0$ [persons]

* $A(0) = 0$ [persons]

* $R(0) = 0$ [persons]

* $\beta(0) = 1$ [unitless]


### Constants

* $\sigma^-1 = 3$ [days]

* $\gamma^-1 = 3$ [days]

* $\alpha = 0.1$ [days]

* $\mu = 0.5$ [unitless]

* $\omega = 0.7$ [unitless]

* $\eta^-1 = 2.1$ [days]

* $\kappa^-1 = 5$ [days]

* $\boldsymbol{\zeta = ?}$ [Persons / day]


```{r unmodelled_predictors}
N_val       <- 4999970

B_guess  <- 3 / 5
P_guess     <- 1

gamma_val   <- 1 / 3 # Clinical
sigma_val   <- 1 / 3
rho_val     <- 1
alpha_val   <- 0.1
mu_val      <- 1 / 2 # Relative infectiousness
omega_val   <- 0.7 # Clinical fraction
eta_val     <- 1 / 2.1 # Preclinical
kappa_val   <- 1 / 5 # Subclinical

fixed_pars <- c(N = N_val, mu = mu_val, omega = omega_val, gamma = gamma_val,
                  sigma = sigma_val, alpha = alpha_val, eta = eta_val, 
                  kappa = kappa_val, rho = rho_val)

unknown_pars <- c(B_0 = B_guess, P_0 = P_guess)

params <- c(fixed_pars, unknown_pars)
```

## Measurement model

\begin{equation}
  y_1 \sim Pois(x_1) 
\end{equation}



```{r}
source("./R_scripts/POMP_models.R")

obs_df    <- irish_data %>% select(-date)
SEI3R_GBM <- get_POMP_model(obs_df, params)
```

# Exploratory analysis

```{r}
tic()
set.seed(1930)
pomp_sims <- pomp::simulate(SEI3R_GBM, nsim = 12000) 
sims_df  <- as.data.frame(pomp_sims)
toc()
```
## Predicted true incidences ($x(t)$)

```{r, fig.height = 3}
ggplot(sims_df, aes(x = time, y = C)) +
  geom_line(aes(group = .id), colour = "grey50", alpha = 0.5) +
  scale_y_continuous(labels = comma) +
  labs(y = "Incidence [new cases per day]",
       subtitle = "Number of simulations = 12,000") +
  geom_point(data = irish_data, aes(x = time, y = y), colour = "red", 
             size = 0.5) +
  theme_pubclean() +
  theme(plot.subtitle = element_text(size = 8, colour = "grey60"))
```

## Predicted effective contact rate ($\zeta \beta(t)$)

```{r, fig.height = 3}
ggplot(sims_df, aes(x = time, y = B * zeta_guess)) +
  geom_line(aes(group = .id), colour = "grey50", alpha = 0.5) +
  scale_y_continuous(labels = comma) +
  labs(y = "Effective contact rate [People / day]",
       subtitle = "Number of simulations = 12,000") +
  theme_pubclean() +
  theme(plot.subtitle = element_text(size = 8, colour = "grey60"))
```

## Final epidemic size

```{r, warning = FALSE}
brs <- c(0,10 ** (2:6), Inf)

lbls <- c("0-10^2", "10^2-10^3", "10^3-10^4", "10^4-10^5",
          "10^5-10^6", "10^6+")

sim_tc_df <- sims_df %>% 
  group_by(.id) %>% summarise(total_C = sum(C), .groups = "drop") %>% 
  mutate(magnitude_order = cut(total_C, breaks = brs, labels = lbls,
                               include.lowest = TRUE,
                               right = FALSE),
         colour = ifelse(magnitude_order == "10^4-10^5", TRUE, FALSE))

ggplot(sim_tc_df, aes(x = magnitude_order)) +
  geom_histogram(stat = "count", aes(fill = colour)) +
  scale_fill_manual(values = c("grey60", "steelblue")) +
  labs(y = "Count", x = "Final epidemic size") +
  theme_pubclean() +
  theme(legend.position = "none")
```

```{r}
ids <- sim_tc_df %>% 
  filter(magnitude_order == "10^4-10^5") %>% pull(.id)

filtered_runs <- sims_df %>% 
  filter(.id %in% ids) %>%
  group_by(.id) %>% 
  mutate(max_C = max(C)) %>% 
  ungroup() %>% 
  filter(max_C < 2000)

ggplot(filtered_runs, aes(x = time, y = C)) +
  geom_line(aes(group = .id), colour = "grey50", alpha = 0.5) +
  geom_point(data = irish_data, aes(x = time, y = y), colour = "red") +
  theme_pubclean()
```

```{r}
ggplot(filtered_runs, aes(x = time, y = B)) +
  geom_line(aes(group = .id), colour = "grey50", alpha = 0.5) +
  theme_pubclean()
```


## Likelihood

```{r}
registerDoParallel(cores = 6)
registerDoRNG(652643293)

foreach (i = 1:10, .combine = c) %dopar% {
  SEI3R_GBM %>% pfilter(Np = 5000)
} -> pf
logLik(pf) -> ll
logmeanexp(ll, se=TRUE)
```

## Likelihood slices

```{r}
slice_design(
  center= coef(SEI3R_GBM),
  B_0  = rep(seq(from = 0.1, to = 3, length = 40), each = 3),
  P_0   = rep(seq(from = 1, to = 30, length = 40), each = 3)
) -> p

file_path <- "./Saved_objects/Irish_data/SEI3R_GBM/slice_design.rds"

if(!file.exists(file_path)) {
  registerDoParallel(cores = 6)
  registerDoRNG(108028909)

  # 5 mins
  tic.clearlog()
  tic()
  
  foreach (theta = iter(p,"row"), .combine = rbind, .inorder = FALSE) %dopar%
  {
    SEI3R_GBM %>% pfilter(params = theta, Np = 5000) -> pf
    theta$loglik <- logLik(pf)
    theta
  } -> slice_ll
   
  toc(quiet = TRUE, log = TRUE)
  log.lst <- tic.log(format = FALSE)
    
  slice_obj  <- list(ll = slice_ll, time = log.lst)
  saveRDS(slice_obj, file_path)
} else {
  slice_obj <- readRDS(file_path)
}

slice_ll <- slice_obj$ll
```

```{r}
slice_ll %>% 
  filter(!is.infinite(loglik), loglik > max(loglik) - 1000) %>% 
  gather(variable, value, B_0, P_0) %>%
  filter(variable == slice) %>%
  ggplot(aes(x = value, y = loglik, color = variable))+
  geom_point() +
  facet_grid(~variable, scales = "free_x", labeller = label_parsed)+
  guides(color = FALSE) +
  labs(x="Parameter value",color="") +
  theme_pubr()
```


```{r, lik_surface}
source("./R_scripts/likelihood_slice.R")
source("./R_scripts/helpers.R")

params_bounds <- list(list(name = "P_0", min = 1, max = 30),
                      list(name = "B_0", min = 0.1, max = 3))

combinations  <- combn(1:length(params_bounds), 2, simplify = FALSE)

folder <- "./Saved_objects/Irish_data/SEI3R_GBM/"

p_list <- likelihood_slice(SEI3R_GBM, combinations, folder) 
```

```{r}
loglik_df <- p_list[[1]]$p %>% select(B_0, P_0, loglik)
  
loglik_df %>%  
  mutate(loglik=ifelse(loglik>max(loglik)-1000,loglik,NA)) %>% 
  ggplot(aes(x= B_0, y= P_0,z=loglik,fill=loglik))+
  geom_tile(color=NA)+
  scale_fill_viridis_c()+
  theme_classic() +
  labs(x=expression(B(0)), y = expression(P(0)))
```
# Local search

```{r}
file_path <- "./Saved_objects/Irish_data/SEI3R_GBM/local_search.rds"

if(!file.exists(file_path)) {
  tic.clearlog()
  tic()
  registerDoRNG(482947940)

  foreach(i = 1:20,.combine = c) %dopar% {

    SEI3R_GBM %>%
        mif2(
          params = params,
          Np = 2000, Nmif = 50,
          cooling.fraction.50 = 0.5,
          rw.sd=rw.sd(B_0 = ivp(0.02), P_0 = ivp(0.02))
        )
    } -> mifs_local
  toc(quiet = TRUE, log = TRUE)
  log.lst <- tic.log(format = FALSE)
  result_list  <- list(result = mifs_local, time = log.lst)
  saveRDS(result_list, file_path)
} else {
  result_list <- readRDS(file_path)
}

mifs_local <- result_list$result
```

```{r}
mifs_local %>%
  traces() %>%
  melt() %>%
  ggplot(aes(x= iteration,y = value,group = L1,color = factor(L1)))+
  geom_line()+
  guides(color=FALSE)+
  facet_wrap(~variable,scales="free_y")
```

```{r}
file_path <- "./Saved_objects/Irish_data/SEI3R_GBM/local_search_likelihood.rds"

if(!file.exists(file_path)) {
  registerDoParallel(cores = detectCores() - 2)
  registerDoRNG(900242057)
  #16 mins
  tic()

  foreach(mf=mifs_local,.combine=rbind) %dopar% {
    evals <- replicate(10, logLik(pfilter(mf,Np=20000)))
    ll <- logmeanexp(evals,se=TRUE)
    mf %>% coef() %>% bind_rows() %>%
      bind_cols(loglik=ll[1],loglik.se=ll[2])
  } -> results
  
  toc()
  saveRDS(results, file_path)
} else {
  results <- readRDS(file_path)
}
```

```{r}
pairs(~loglik+B_0+P_0, data = results, pch = 16)
```

# Global search

```{r}
file_path <- "./Saved_objects/Irish_data/SEI3R_GBM/Global_search.rds"

set.seed(2062379496)

runif_design(
  lower = c(B_0 = 0.1, P_0 = 1),
  upper = c(B_0 = 3, P_0 = 30),
  nseq  = 300
) -> guesses

fixed_params <- params[c("N", "gamma", "sigma", "alpha", "mu", "eta", "kappa", "rho", "omega")]

if(!file.exists(file_path)) {
  mf1 <- mifs_local[[1]]

  registerDoParallel(cores = detectCores() - 2)
  registerDoRNG(1270401374)

  # 14 hours
  tic()

  foreach(guess=iter(guesses,"row"), .combine=rbind) %dopar% {
    mf1 %>%
      mif2(params = c(unlist(guess), fixed_params)) %>%
      mif2(Nmif = 100) -> mf
    
    replicate(
      10,
      mf %>% pfilter(Np = 100000) %>% logLik()
    ) %>%
      logmeanexp(se=TRUE) -> ll
    
    mf %>% coef() %>% bind_rows() %>%
      bind_cols(loglik = ll[1],loglik.se=ll[2])
  } -> results
toc()
saveRDS(results, file_path)
} else {
  results <- readRDS(file_path)  
}
```

```{r}
results %>% filter(loglik>max(loglik)- 500) %>%
  bind_rows(guesses) %>%
  mutate(type=if_else(is.na(loglik),"guess","result")) %>%
  arrange(type) -> all

pairs(~loglik +B_0 + P_0, data=all,
      col=ifelse(all$type=="guess",grey(0.5),"red"),pch=16)
```

```{r}
all %>%
  filter(type == "result") %>%
#  filter(loglik>max(loglik)-100) %>%
  ggplot(aes(x = B_0,y = loglik))+
  geom_point()+
  labs(
    x=expression("B[0]"),
    title="poor man's profile likelihood"
  )
```


```{r}
filter(all, type == "result") %>% 
  select(-type) %>% 
  filter(loglik > max(loglik)-50) %>%
  sapply(range) -> box

set.seed(1196696958)

profile_design(
  B_0   = seq(0.25, 2.00,length = 40),
  lower = box[1,c("P_0")],
  upper = box[2,c("P_0")],
  nprof=15, type="runif"
) -> guesses
plot(guesses)
```

```{r}
filename <- "./Saved_objects/Irish_data/SEI3R_GBM/Beta_profile.rds"

if(!file.exists(filename)) {
  mf1 <- mifs_local[[1]]
registerDoRNG(830007657)

tic()
foreach(guess=iter(guesses,"row"), .combine=rbind) %dopar% {
  mf1 %>%
    mif2(params = c(unlist(guess),fixed_params),
         rw.sd = rw.sd(P_0 = ivp(0.02))) %>%
      mif2(Nmif = 100, cooling.fraction.50 = 0.3) -> mf
    replicate(
      10,
      mf %>% pfilter(Np = 100000) %>% logLik()) %>%
      logmeanexp(se=TRUE) -> ll
    mf %>% coef() %>% bind_rows() %>%
      bind_cols(loglik=ll[1],loglik.se=ll[2])
  } -> results
toc()
saveRDS(results, filename)
} else {
  results <- readRDS(filename)
}
```

```{r}
filter(results, 
       loglik.se < 2) %>% 
  filter(loglik>max(loglik)-100) -> all

pairs(~loglik+B_0+P_0,data=all,pch=16)
```

```{r}
results %>%
  ggplot(aes(x=B_0,y=loglik))+
  geom_point()
```

```{r}
top_10 <- all %>% arrange(desc(loglik)) %>% 
  slice(1:10) %>% select(B_0, P_0)

filename <- "./Saved_objects/Irish_data/SEI3R_GBM/pf_top_10.rds"

if(!file.exists(filename)) {
  registerDoParallel(cores = 6)
  registerDoRNG(824210306)

  foreach(guess = iter(top_10,"row"), .combine = c) %dopar% {
    SEI3R_GBM %>% 
      pfilter(Np = 200000,
              params = c(unlist(guess), fixed_params),
              filter.mean = TRUE, pred.mean = TRUE)
  } -> pfs
  
  saveRDS(pfs, filename)
} else {
  pfs <- readRDS(filename)
}
```




```{r}
imap_dfr(pfs, function(pf, i) {
  pred_mean_B     <- pred.mean(pf)["B" ,]
  
  data.frame(iter = i, time = 1:79, B = pred_mean_B)
}) -> B_pf
```

```{r}
ggplot(B_pf, aes(x = time, y = B)) +
  geom_line(aes(group = iter, colour = as.factor(iter))) +
  theme_pubclean()
```


```{r}
ggplot(B_pf, aes(x = time, y = B)) +
  geom_line(aes(group = iter, colour = as.factor(iter))) +
  facet_wrap(~iter) +
  theme_pubclean() +
  theme(legend.position = "none")
```
```{r}
first_val <- B_pf %>% filter(time == 1) %>% 
  rename(normaliser = B) %>% 
  select(iter, normaliser)

B_norm <- B_pf %>% left_join(first_val, by = "iter") %>% 
  mutate(index = B / normaliser)
```

```{r}
apple_data <- get_apple_data(start_date = "2020-02-29",
                             end_date = "2020-05-17")

driving_data <- filter(apple_data, transportation_type == "driving")
first_val    <- driving_data[1, "index"] %>% as.numeric()

driving_data <- driving_data %>% mutate(index = index / first_val,
                                        time = row_number())
```
```{r}
split_df <- split(B_norm, B_norm$iter)

imap_dfr(split_df, function(df, i) {
  cor <- cor.test(x = diff(df$index), y = diff(driving_data$index), method = 'pearson',
                  exact = FALSE)
  
  cor1 <- cor.test(x = diff(df$index), y = diff(driving_data$index), method = 'spearman',
                  exact = FALSE)
  
  data.frame(iter = i, pearson_cor = cor$estimate, 
             pearson_p_value = cor$p.value, spearman_cor = cor1$estimate,
             spearman_p_value = cor1$p.value)
}) %>% mutate(x = 37, index = 1) -> cor_df

```



```{r}
ggplot(B_norm, aes(x = time, y = index)) +
  geom_line(aes(group = iter, colour = as.factor(iter))) +
  facet_wrap(~iter, scales = "free") +
  geom_line(data = driving_data, aes(x = time, y= index), colour = "grey45") +
  geom_text(data = cor_df, aes(x = x, label = round(pearson_cor, 2)),
            size = 3) +
  theme_pubclean() +
  theme(legend.position = "none")
```


```{r}
imap_dfr(pfs, function(pf, i) {
  pred_mean_C     <- pred.mean(pf)["C" ,]
  
  data.frame(iter = i, time = 1:79, C = pred_mean_C)
}) -> C_df
```

```{r}
ggplot(C_df, aes(x = time, y = C)) +
  geom_line(aes(group = iter, colour = as.factor(iter))) +
  geom_point(data = irish_data, aes(x = time, y = y)) +
  theme_pubclean()
```

```{r}
imap_dfr(pfs, function(pf, i) {
  pred_mean_R     <- pred.mean(pf)["R" ,]
  
  data.frame(iter = i, time = 1:79, R = pred_mean_R)
}) -> R_df
```

```{r}
ggplot(R_df, aes(x = time, y = R)) +
  geom_line(aes(group = iter, colour = as.factor(iter))) +
  theme_pubclean()
```

```{r}
raw_data <- driving_data$index

ggplot_na_distribution(raw_data)
```

```{r}
imp <- na_interpolation(raw_data)
ggplot_na_imputations(raw_data, imp)
```

```{r}
irish_data2 <- irish_data %>% mutate(y2 = imp) %>% 
  rename(y1 = y)
tau_val     <- 1
```



```{r}
Csnippet("
  y1  = rpois(C);  
  y2 = rnorm(B, tau);
  ") -> rmeas

Csnippet("
  lik = dpois(y1,C,give_log) + dnorm(y2, B, tau, give_log);
") -> dmeas

Csnippet("
  S = 4999970 - P_0;
  E = 0;
  P = P_0;
  I = 0;
  A = 0;
  R = 0;
  B = 1;
  C = 0;
  ") -> rinit

Csnippet("
  double dW     = rnorm(0,sqrt(dt));
  double lambda = B_0 * B * (I + P + mu * A) / N;
  S-= (S * lambda)*dt;
  E+= (S * lambda - sigma*E)*dt;
  P+= (omega * sigma * E - eta * P) * dt;
  I+= (eta * P - gamma*I)*dt;
  R+= (gamma*I + kappa * A)*dt;
  A+= ((1-omega) * sigma * E - kappa * A) * dt;
  B+= alpha*B*dW;
  C+= (rho*eta*P)*dt;
") -> SEI3R_GBM_step2

params <- c(N = N_val, mu = mu_val, omega = omega_val, gamma = gamma_val, 
            B_0 = B_guess, sigma = sigma_val, alpha = alpha_val, eta = eta_val,
            P_0 = P_guess, kappa = kappa_val, rho = rho_val,
            tau = tau_val)

par_names <- names(params)

irish_data2 %>% select(-date) %>% 
pomp(
  times = "time", t0 = 0,
  rinit = rinit,
  rprocess = pomp::euler(SEI3R_GBM_step2, delta.t = 0.01),
  statenames = c("S", "E", "P","I", "R", "A", "C", "B"),
  paramnames = par_names,
  params = params,
  accumvars = "C",
  rmeasure = rmeas,
  dmeasure = dmeas,
  partrans = parameter_trans(log   = c("B_0", "P_0", "tau")),
  obsnames = c("y1", "y2")
) -> SEI3R_GBM2
```

```{r}
set.seed(1832)
pomp_sims  <- pomp::simulate(SEI3R_GBM2, nsim = 10000) 
prior_runs <- as.data.frame(pomp_sims)
```

```{r, warning = FALSE}
brs <- c(0,10 ** (2:6), Inf)

lbls <- c("0-10^2", "10^2-10^3", "10^3-10^4", "10^4-10^5",
          "10^5-10^6", "10^6+")

sim_tc_df <- prior_runs %>% 
  group_by(.id) %>% summarise(total_C = sum(C), .groups = "drop") %>% 
  mutate(magnitude_order = cut(total_C, breaks = brs, labels = lbls,
                               include.lowest = TRUE,
                               right = FALSE))

ggplot(sim_tc_df, aes(x = magnitude_order)) +
  geom_histogram(stat = "count") +
  theme_pubclean()
```

```{r}
ids <- sim_tc_df %>% 
  filter(magnitude_order == "10^4-10^5") %>% pull(.id)

filtered_runs <- prior_runs  %>% 
  filter(.id %in% ids) %>%
  group_by(.id) %>% 
  mutate(max_C = max(C)) %>% 
  ungroup() %>% 
  filter(max_C < 2000)

ggplot(filtered_runs, aes(x = time, y = C)) +
  geom_line(aes(group = .id), colour = "grey50", alpha = 0.5) +
  geom_point(data = irish_data, aes(x = time, y = y), colour = "red") +
  theme_pubclean()
```

```{r}
ggplot(filtered_runs, aes(x = time, y = B)) +
  geom_line(aes(group = .id), colour = "grey50", alpha = 0.5) +
  geom_point(data = irish_data2, aes(y = y2), colour = "red") +
  theme_pubclean()
```

## Likelihood

```{r}
registerDoParallel(cores = 6)
registerDoRNG(652643293)

foreach (i = 1:10, .combine = c) %dopar% {
  SEI3R_GBM2 %>% pfilter(Np = 5000)
} -> pf
logLik(pf) -> ll
logmeanexp(ll, se=TRUE)
```


# Local search

```{r}
file_path <- "./Saved_objects/Irish_data/SEI3R_GBM/local_search2.rds"

if(!file.exists(file_path)) {
  tic.clearlog()
  tic()
  registerDoRNG(482947940)

  foreach(i = 1:20,.combine = c) %dopar% {

    SEI3R_GBM2 %>%
        mif2(
          params = params,
          Np = 2000, Nmif = 50,
          cooling.fraction.50 = 0.5,
          rw.sd=rw.sd(B_0 = 0.02, P_0 = ivp(0.02),
                      tau = 0.02)
        ) %>% mif2(Nmif = 100) %>% 
      mif2(Nmif=100,cooling.fraction.50=0.3) %>%
      mif2(Nmif=100,cooling.fraction.50=0.1)
    } -> mifs_local
  toc(quiet = TRUE, log = TRUE)
  log.lst <- tic.log(format = FALSE)
  result_list  <- list(result = mifs_local, time = log.lst)
  saveRDS(result_list, file_path)
} else {
  result_list <- readRDS(file_path)
}

mifs_local <- result_list$result
```

```{r}
mifs_local %>%
  traces() %>%
  melt() -> traces_df 

traces_df %>%
  ggplot(aes(x= iteration,y = value,group = L1,color = factor(L1)))+
  geom_line()+
  guides(color=FALSE)+
  facet_wrap(~variable,scales="free_y")
```

```{r}
traces_df %>% filter(variable == "loglik") %>% 
  ggplot(aes(x = iteration, y = value)) +
  geom_line() +
  facet_wrap(~L1, scales = "free")
```

```{r}
file_path <- "./Saved_objects/Irish_data/SEI3R_GBM/local_search_likelihood2.rds"

if(!file.exists(file_path)) {
  registerDoParallel(cores = detectCores() - 2)
  registerDoRNG(900242057)
  #16 mins
  tic()

  foreach(mf=mifs_local,.combine=rbind) %dopar% {
    evals <- replicate(10, logLik(pfilter(mf, Np = 20000)))
    ll <- logmeanexp(evals,se=TRUE)
    mf %>% coef() %>% bind_rows() %>%
      bind_cols(loglik=ll[1],loglik.se=ll[2])
  } -> results
  
  toc()
  saveRDS(results, file_path)
} else {
  results <- readRDS(file_path)
}
```

```{r}
pairs(~loglik+B_0+P_0+tau, data = results, pch = 16)
```

# Global search

```{r}
file_path <- "./Saved_objects/Irish_data/SEI3R_GBM/Global_search2.rds"

set.seed(58741564)

runif_design(
  lower = c(B_0 = 0.1, P_0 = 1, tau = 0.05),
  upper = c(B_0 = 3, P_0 = 30, tau = 3),
  nseq  = 300
) -> guesses

fixed_params <- params[c("N", "gamma", "sigma", "alpha", "mu", "eta", "kappa", "rho", "omega")]

if(!file.exists(file_path)) {
  mf1 <- mifs_local[[1]]

  registerDoParallel(cores = detectCores() - 2)
  registerDoRNG(1270401374)

  # 14 hours
  tic()

  foreach(guess=iter(guesses,"row"), .combine=rbind) %dopar% {
    mf1 %>%
      mif2(params = c(unlist(guess), fixed_params)) %>%
      mif2(Nmif = 100) -> mf
    
    replicate(
      10,
      mf %>% pfilter(Np = 100000) %>% logLik()
    ) %>%
      logmeanexp(se=TRUE) -> ll
    
    mf %>% coef() %>% bind_rows() %>%
      bind_cols(loglik = ll[1],loglik.se=ll[2])
  } -> results
toc()
saveRDS(results, file_path)
} else {
  results <- readRDS(file_path)  
}
```

```{r}
results %>% #filter(loglik>max(loglik)- 50) %>%
  bind_rows(guesses) %>%
  mutate(type=if_else(is.na(loglik),"guess","result")) %>%
  arrange(type) -> all

pairs(~loglik +B_0 + P_0, data=all,
      col=ifelse(all$type=="guess",grey(0.5),"red"),pch=16)
```

```{r}
all %>%
  filter(type == "result") %>%
#  filter(loglik>max(loglik) - 50) %>%
  ggplot(aes(x = B_0,y = loglik))+
  geom_point()+
  labs(
    x=expression("B[0]"),
    title="poor man's profile likelihood"
  )
```