---
title: "S2 Appendix"
output:
  pdf_document: 
    number_sections: true
header-includes:
  - \usepackage{booktabs}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(cmdstanr)
library(dplyr)
library(extraDistr)
library(imputeTS)
library(kableExtra)
library(lubridate)
library(Metrics)
library(purrr)
library(readr)
library(readsdr)
library(readxl)
library(rstan)
library(stringr)
library(tictoc)
library(tidyr)

folder      <- "./Saved_objects/Irish_data/SEI3R_SMTH"
stan_folder <- "./Stan_files"
```

# Data

```{r}
source("./R_scripts/irish_data.R")
irish_data   <- get_irish_data()

source("./R_scripts/apple.R")
drv_data_obj <- get_driving_data()
```

```{r, fig.height = 3}
source("./R_scripts/plots.R")

plot_daily_data(irish_data, drv_data_obj$df)
```


# Priors

```{r, fig.height = 3}
source("./R_scripts/plots.R")
plot_priors()
```

# Inference

```{r inference_lists}
source("./R_scripts/stan_utils.R")
source("./R_scripts/write_SEI3R_model.R")
n_orders            <- 9
posterior_list      <- vector("list", n_orders)
sim_incidences_list <- vector("list", n_orders)
Z_list              <- vector("list", n_orders)
ll_list             <- vector("list", n_orders)
time_list           <- vector("list", n_orders)
```


## 1st order delay

```{r}
dly_o <- 1 # delay order

mdl_path  <- str_glue("./models/SEI3R_order_{dly_o}.stmx")
mdl       <- read_xmile(mdl_path)
stocks    <- sd_stocks(mdl)
stan_path <- str_glue("./Stan_files/SEI3R_{dly_o}_smth.stan")
write_SEI3R_model(mdl_path, stan_path)
```

```{r fit_SMTH_1}
stan_d <- list(n_obs    = nrow(irish_data),
               y1       = irish_data$y,
               n_params = 3,
               n_difeq  = nrow(stocks),
               t0       = 0,
               ts       = 1:nrow(irish_data))

fit_options <- list(stan_d      = stan_d,
                    seed        = 931918239,
                    warmup      = 4000,
                    sampling    = 2000,
                    adapt_delta = 0.90,
                    step_size   = 0.0001) # default

results            <- run_stan_file(dly_o, fit_options, folder, stan_folder)
time_list[[dly_o]] <- calculate_time(results$time)
sf                 <- results$sf
```

### Traceplots

```{r, fig.height = 3.5}
traceplot(sf, pars = c("zeta", "nu", "upsilon", "P_0"))
```

```{r}
posterior_df                 <- as.data.frame(sf)
posterior_list[[dly_o]]      <- posterior_df
sim_incidences_list[[dly_o]] <- construct_incidence_df(posterior_df)
Z_list[[dly_o]]              <- extract_timeseries_stock("Z", posterior_df,
                                                         stocks, "o")
ll_list[[dly_o]]             <- posterior_df %>% select(log_lik)
```

## 2nd order delay

```{r}
dly_o <- 2 # delay order

mdl_path  <- str_glue("./models/SEI3R_order_{dly_o}.stmx")
mdl       <- read_xmile(mdl_path)
stocks    <- sd_stocks(mdl)
stan_path <- str_glue("./Stan_files/SEI3R_{dly_o}_smth.stan")
write_SEI3R_model(mdl_path, stan_path)
```

```{r fit_SMTH_2}
stan_d <- list(n_obs    = nrow(irish_data),
               y1       = irish_data$y,
               n_params = 3,
               n_difeq  = nrow(stocks),
               t0       = 0,
               ts       = 1:nrow(irish_data))

fit_options <- list(stan_d      = stan_d,
                    seed        = 693132317,
                    warmup      = 2000,
                    sampling    = 2000,
                    adapt_delta = 0.95, # default
                    step_size   = 0.0001) 

results            <- run_stan_file(dly_o, fit_options, folder, stan_folder)
time_list[[dly_o]] <- calculate_time(results$time)
sf                 <- results$sf
```

### Traceplots

```{r, fig.height = 3.5}
traceplot(sf, pars = c("zeta", "nu", "upsilon", "P_0"))
```

```{r}
posterior_df                 <- as.data.frame(sf)
posterior_list[[dly_o]]      <- posterior_df
sim_incidences_list[[dly_o]] <- construct_incidence_df(posterior_df)
Z_list[[dly_o]]              <- extract_timeseries_stock("Z", posterior_df,
                                                         stocks, "o")
ll_list[[dly_o]]             <- posterior_df %>% select(log_lik)
```

## 3rd order delay

```{r}
dly_o <- 3 # delay order

mdl_path  <- str_glue("./models/SEI3R_order_{dly_o}.stmx")
mdl       <- read_xmile(mdl_path)
stocks    <- sd_stocks(mdl)
stan_path <- "./Stan_files/SEI3R_3_smth.stan"
write_SEI3R_model(mdl_path, stan_path)
```

```{r fit_SMTH_3}
stan_d <- list(n_obs    = nrow(irish_data),
               y1       = irish_data$y,
               n_params = 3,
               n_difeq  = nrow(stocks),
               t0       = 0,
               ts       = 1:nrow(irish_data))

fit_options <- list(stan_d      = stan_d,
                    seed        = 477626707,
                    warmup      = 2000,
                    sampling    = 2000,
                    step_size   = 0.0001,
                    adapt_delta = 0.95) # default

results            <- run_stan_file(dly_o, fit_options, folder, stan_folder)
time_list[[dly_o]] <- calculate_time(results$time)
sf                 <- results$sf
```

### Traceplots

```{r, fig.height = 3.5}
traceplot(sf, pars = c("zeta", "nu", "upsilon", "P_0"))
```

```{r}
posterior_df                 <- as.data.frame(sf)
posterior_list[[dly_o]]      <- posterior_df
sim_incidences_list[[dly_o]] <- construct_incidence_df(posterior_df)
Z_list[[dly_o]]              <- extract_timeseries_stock("Z", posterior_df,
                                                         stocks, "o")
ll_list[[dly_o]]             <- posterior_df %>% select(log_lik)
```


## 4th order delay

```{r}
dly_o <- 4 # delay order

mdl_path  <- str_glue("./models/SEI3R_order_{dly_o}.stmx")
mdl       <- read_xmile(mdl_path)
stocks    <- sd_stocks(mdl)
stan_path <- str_glue("./Stan_files/SEI3R_{dly_o}_smth.stan")
write_SEI3R_model(mdl_path, stan_path)
```

```{r fit_SMTH_4}
stan_d <- list(n_obs    = nrow(irish_data),
               y1       = irish_data$y,
               n_params = 3,
               n_difeq  = nrow(stocks),
               t0       = 0,
               ts       = 1:nrow(irish_data))

fit_options <- list(stan_d      = stan_d,
                    seed        = 986614638,
                    warmup      = 2000,
                    sampling    = 2000,
                    step_size   = 0.001,
                    adapt_delta = 0.8) # default

results            <- run_stan_file(dly_o, fit_options, folder, stan_folder)
time_list[[dly_o]] <- calculate_time(results$time)
sf                 <- results$sf
```

### Traceplots

```{r, fig.height = 3.5}
traceplot(sf, pars = c("zeta", "nu", "upsilon", "P_0"))
```

```{r}
posterior_df                 <- as.data.frame(sf)
posterior_list[[dly_o]]      <- posterior_df
sim_incidences_list[[dly_o]] <- construct_incidence_df(posterior_df)
Z_list[[dly_o]]              <- extract_timeseries_stock("Z", posterior_df,
                                                         stocks, "o")
ll_list[[dly_o]]             <- posterior_df %>% select(log_lik)
```


## 5th order delay

```{r}
dly_o <- 5 # delay order

mdl_path  <- str_glue("./models/SEI3R_order_{dly_o}.stmx")
mdl       <- read_xmile(mdl_path)
stocks    <- sd_stocks(mdl)
stan_path <- str_glue("./Stan_files/SEI3R_{dly_o}_smth.stan")
write_SEI3R_model(mdl_path, stan_path)
```

```{r fit_SMTH_5}
stan_d <- list(n_obs    = nrow(irish_data),
               y1       = irish_data$y,
               n_params = 3,
               n_difeq  = nrow(stocks),
               t0       = 0,
               ts       = 1:nrow(irish_data))

fit_options <- list(stan_d      = stan_d,
                    seed        = 549943389,
                    warmup      = 2000,
                    sampling    = 2000,
                    step_size   = 0.001,
                    adapt_delta = 0.8) # default

results            <- run_stan_file(dly_o, fit_options, folder, stan_folder)
time_list[[dly_o]] <- calculate_time(results$time)
sf                 <- results$sf
```

### Traceplots

```{r, fig.height = 3.5}
traceplot(sf, pars = c("zeta", "nu", "upsilon", "P_0"))
```

```{r}
posterior_df                 <- as.data.frame(sf)
posterior_list[[dly_o]]      <- posterior_df
sim_incidences_list[[dly_o]] <- construct_incidence_df(posterior_df)
Z_list[[dly_o]]              <- extract_timeseries_stock("Z", posterior_df,
                                                         stocks, "o")
S_df                         <- extract_timeseries_stock("S", posterior_df,
                                                         stocks, "o")
ll_list[[dly_o]]             <- posterior_df %>% select(log_lik)
```


## 6th order delay

```{r}
dly_o <- 6 # delay order

mdl_path  <- str_glue("./models/SEI3R_order_{dly_o}.stmx")
mdl       <- read_xmile(mdl_path)
stocks    <- sd_stocks(mdl)
stan_path <- str_glue("./Stan_files/SEI3R_{dly_o}_smth.stan")
write_SEI3R_model(mdl_path, stan_path)
```

```{r fit_SMTH_6}
stan_d <- list(n_obs    = nrow(irish_data),
               y1       = irish_data$y,
               n_params = 3,
               n_difeq  = nrow(stocks),
               t0       = 0,
               ts       = 1:nrow(irish_data))

fit_options <- list(stan_d      = stan_d,
                    seed        = 846206826,
                    warmup      = 2000,
                    sampling    = 2000,
                    adapt_delta = 0.90, # default
                    step_size   = 0.001) 

results            <- run_stan_file(dly_o, fit_options, folder, stan_folder)
time_list[[dly_o]] <- calculate_time(results$time)
sf                 <- results$sf
```

### Traceplots

```{r, fig.height = 3.5}
traceplot(sf, pars = c("zeta", "nu", "upsilon", "P_0"))
```

```{r}
posterior_df                 <- as.data.frame(sf)
posterior_list[[dly_o]]      <- posterior_df
sim_incidences_list[[dly_o]] <- construct_incidence_df(posterior_df)
Z_list[[dly_o]]              <- extract_timeseries_stock("Z", posterior_df,
                                                         stocks, "o")
ll_list[[dly_o]]             <- posterior_df %>% select(log_lik)
```

## 7th order delay

```{r}
dly_o <- 7 # delay order

mdl_path  <- str_glue("./models/SEI3R_order_{dly_o}.stmx")
mdl       <- read_xmile(mdl_path)
stocks    <- sd_stocks(mdl)
stan_path <- str_glue("./Stan_files/SEI3R_{dly_o}_smth.stan")
write_SEI3R_model(mdl_path, stan_path)
```

```{r fit_SMTH_7}
stan_d <- list(n_obs    = nrow(irish_data),
               y1       = irish_data$y,
               n_params = 3,
               n_difeq  = nrow(stocks),
               t0       = 0,
               ts       = 1:nrow(irish_data))

fit_options <- list(stan_d      = stan_d,
                    seed        = 373573480,
                    warmup      = 2000,
                    sampling    = 2000,
                    adapt_delta = 0.95, # default
                    step_size   = 0.0001) 

results            <- run_stan_file(dly_o, fit_options, folder, stan_folder)
time_list[[dly_o]] <- calculate_time(results$time)
sf                 <- results$sf
```

### Traceplots

```{r, fig.height = 3.5}
traceplot(sf, pars = c("zeta", "nu", "upsilon", "P_0"))
```

```{r}
posterior_df                 <- as.data.frame(sf)
posterior_list[[dly_o]]      <- posterior_df
sim_incidences_list[[dly_o]] <- construct_incidence_df(posterior_df)
Z_list[[dly_o]]              <- extract_timeseries_stock("Z", posterior_df,
                                                         stocks, "o")
ll_list[[dly_o]]             <- posterior_df %>% select(log_lik)
```

## 8th order delay

```{r}
dly_o <- 8 # delay order

mdl_path  <- str_glue("./models/SEI3R_order_{dly_o}.stmx")
mdl       <- read_xmile(mdl_path)
stocks    <- sd_stocks(mdl)
stan_path <- str_glue("./Stan_files/SEI3R_{dly_o}_smth.stan")
write_SEI3R_model(mdl_path, stan_path)
```

```{r fit_SMTH_8}
stan_d <- list(n_obs    = nrow(irish_data),
               y1       = irish_data$y,
               n_params = 3,
               n_difeq  = nrow(stocks),
               t0       = 0,
               ts       = 1:nrow(irish_data))

fit_options <- list(stan_d      = stan_d,
                    seed        = 107900538,
                    warmup      = 4000,
                    sampling    = 2000,
                    adapt_delta = 0.80, # default
                    step_size   = 0.001) 

results            <- run_stan_file(dly_o, fit_options, folder, stan_folder)
time_list[[dly_o]] <- calculate_time(results$time)
sf                 <- results$sf
```

```{r, fig.height = 3.5}
traceplot(sf, pars = c("zeta", "nu", "upsilon", "P_0"))
```

```{r}
posterior_df                 <- as.data.frame(sf)
posterior_list[[dly_o]]      <- posterior_df
sim_incidences_list[[dly_o]] <- construct_incidence_df(posterior_df)
Z_list[[dly_o]]              <- extract_timeseries_stock("Z", posterior_df,
                                                         stocks, "o")
ll_list[[dly_o]]             <- posterior_df %>% select(log_lik)
```

## 9th order delay

```{r}
dly_o <- 9 # delay order

mdl_path  <- str_glue("./models/SEI3R_order_{dly_o}.stmx")
mdl       <- read_xmile(mdl_path)
stocks    <- sd_stocks(mdl)
stan_path <- str_glue("./Stan_files/SEI3R_{dly_o}_smth.stan")
write_SEI3R_model(mdl_path, stan_path)
```

```{r fit_SMTH_9}
stan_d <- list(n_obs    = nrow(irish_data),
               y1       = irish_data$y,
               n_params = 3,
               n_difeq  = nrow(stocks),
               t0       = 0,
               ts       = 1:nrow(irish_data))

fit_options <- list(stan_d      = stan_d,
                    seed        = 790975884,
                    warmup      = 4000,
                    sampling    = 2000,
                    adapt_delta = 0.80, # default
                    step_size   = 0.001) 

results            <- run_stan_file(dly_o, fit_options, folder, stan_folder)
time_list[[dly_o]] <- calculate_time(results$time)
sf                 <- results$sf
```

```{r, fig.height = 3.5}
traceplot(sf, pars = c("zeta", "nu", "upsilon", "P_0"))
```

```{r}
posterior_df                 <- as.data.frame(sf)
posterior_list[[dly_o]]      <- posterior_df
sim_incidences_list[[dly_o]] <- construct_incidence_df(posterior_df)
Z_list[[dly_o]]              <- extract_timeseries_stock("Z", posterior_df,
                                                         stocks, "o")
ll_list[[dly_o]]             <- posterior_df %>% select(log_lik)
```


\newpage

# Summary

## Fits

### Incidence

\hfill

```{r inc_fits_g, fig.height = 7}

set.seed(19860618)
incidence_g <- purrr::map(sim_incidences_list, function(df) {
  
  sample_iters <- sample.int(8000, 100)
  
  df <- df %>% filter(iter %in% sample_iters)
  
  ggplot(df, aes(x = time, y = value)) +
  geom_line(aes(group = iter), colour = "grey50", alpha = 0.1) +
  geom_point(data = irish_data, aes(y = y), colour = "steelblue",
             alpha = 0.8, size = 0.5) +
  theme_pubr() +
  labs(subtitle = str_glue("Order: {unique(df$order)}"),
       x = "")
}) %>% compact()

(incidence_g[[1]] + incidence_g[[2]] + incidence_g[[3]]) / 
  ( incidence_g[[4]] + incidence_g[[5]] + incidence_g[[6]]) /
  (incidence_g[[7]] + incidence_g[[8]] + incidence_g[[9]])

```


```{r, fig.height = 7}
set.seed(19860618)

map_df(sim_incidences_list, function(df) {
    sample_iters <- sample.int(8000, 100)
    df <- df %>% filter(iter %in% sample_iters)
}) -> sample_incidences

imap_dfr(Z_list, function(df, i) {
  sample_iters <- sample.int(8000, 100)
  df           <- df %>% filter(iter %in% sample_iters) %>% 
    mutate(order = i)
}) -> sample_Z

df_labels <- data.frame(x = 6, y = 750, 
                        label = str_glue("Order: {1:9}"),
                        order = 1:9)
y_lab <- "C[t]^d"
x_lab <- "Time since the first reported case [Days]"
g1 <- plot_fits_by_order(sample_incidences, irish_data, df_labels, 18, x_lab,
                         y_lab = y_lab)


actual_data <- rename(drv_data_obj$df, y = y2)
df_labels   <- df_labels %>% mutate(x = 75, y = 0.85)
y_lab       <- "Z[t]"
x_lab       <- "Time since the first reported case [Days]"
g2          <- plot_fits_by_order(sample_Z, actual_data, df_labels, 16,
                                  x_lab, y_lab)

ggsave("./paper_plots/Fig_06_GSB.pdf", 
       plot = g1 + g2, height = 7, width = 5)
```


\newpage

### Mobility fits

\hfill

```{r mob_fits_g, fig.height = 7}
mobility_g <- imap(Z_list, function(df, i) {
  
  sample_iters <- sample.int(8000, 100)
  df           <- df %>% filter(iter %in% sample_iters)
  
  ggplot(df, aes(x = time, y = value)) +
  geom_line(aes(group = iter), colour = STH_colour, alpha = 0.1) +
  theme_pubr() +
  geom_point(data = drv_data_obj$df, aes(y = y2), colour = data_colour, 
             alpha = 0.8, size = 0.5) +
  labs(subtitle = str_glue("Order: {i}"),
       x = "") +
  theme(axis.text = element_text(size = 1),
        plot.subtitle = element_text(size = 1)) 
}) %>% compact()

(mobility_g[[1]] + mobility_g[[2]] + mobility_g[[3]]) / (mobility_g[[4]] + mobility_g[[5]] + mobility_g[[6]]) /
  (mobility_g[[7]] + mobility_g[[8]] + mobility_g[[9]])
```


## Likelihood

```{r}
ll_df <- imap_dfr(ll_list, function(df, i) {
  df %>% mutate(order = i)
})

ggplot(ll_df, aes(x = as.factor(order), y = log_lik)) +
  geom_boxplot() +
  theme_pubr()
```



## Mean Absolute Scaled Error 

```{r}
mase_inc <- imap_dfr(sim_incidences_list, mase_per_iter, 
                     data_vector = irish_data$y)

summary_mase <- mase_inc %>% group_by(order) %>% 
  summarise(mean   = mean(mase),
            q_val  = quantile(mase, c(0.025, 0.25, 0.5, 0.75, 0.975)),
            q_type = c("q2.5", "q25", "q50", "q75", "q97.5")) %>% 
  ungroup()

ggplot(mase_inc, aes(x = order, y = mase)) +
  geom_violin(aes(group = order), colour = STH_colour) +
  scale_x_continuous(breaks = 1:9) +
  scale_y_continuous(limits = c(0.95, 1.01)) +
  stat_smooth(data = summary_mase, aes(x = order, y = mean),
              geom = 'line', alpha = 0.25, se = FALSE, 
              colour = STH_colour, size = 0.5, linetype = "dashed") +
  geom_hline(yintercept = 1, linetype = "dotted", colour = "grey50") +
  theme_pubr() +
  labs(subtitle = "Incidence prediction accuracy",
       y = "MASE [Unitless]",
       x = "Delay order")
```

```{r}
wide_smy_mase <- summary_mase %>% 
  mutate(q_val = round(q_val, 3),
         mean  = round(mean, 3)) %>% 
  pivot_wider(names_from = q_type, values_from = q_val)

knitr::kable(wide_smy_mase, "latex", booktabs = TRUE)
```


```{r, fig.height = 3.5}
mase_mob <- imap_dfr(Z_list, mase_per_iter, 
                     data_vector = drv_data_obj$df$y2)

summary_mase_mob <- mase_mob %>% group_by(order) %>% 
  summarise(mean   = mean(mase),
            q_val  = quantile(mase, c(0.025, 0.25, 0.5, 0.75, 0.975)),
            q_type = c("q2.5", "q25", "q50", "q75", "q97.5")) %>% 
  ungroup()

ggplot(mase_mob, aes(x = order, y = mase)) +
  geom_violin(aes(group = order), colour = STH_colour) +
  scale_x_continuous(breaks = 1:9) +
  stat_smooth(data = summary_mase_mob, aes(x = order, y = mean),
              geom = 'line', alpha = 0.5, se = FALSE, 
              colour = STH_colour, size = 0.5, linetype = "dashed") +
  geom_hline(yintercept = 1, linetype = "dotted", colour = "grey50") +
  theme_pubr() +
  labs(subtitle = "Mobility prediction accuracy",
       x        = "Delay order")
```


```{r}
wide_smy_mob <- summary_mase_mob %>% 
  mutate(q_val = round(q_val, 3),
         mean  = round(mean, 3)) %>% 
  pivot_wider(names_from = q_type, values_from = q_val)

knitr::kable(wide_smy_mob, "latex", booktabs = TRUE)
```

## Estimates

```{r, fig.height = 5}
source("./R_scripts/R_estimates.R")

imap_dfr(posterior_list, function(df, i) {
  
  df %>% select(zeta, P_0, nu, upsilon) %>% 
    mutate(R_0 = estimate_r(zeta), iter = row_number(), order = i) %>% 
    pivot_longer(c(-iter, -order))
}) -> tidy_pars_df


ggplot(tidy_pars_df, aes(x = as.factor(order), y = value)) +
  geom_violin(aes(group = order), colour = STH_colour) +
  facet_wrap(~name, scales = "free", labeller = label_parsed) +
  labs(x = "Delay order", y = "Value") +
  theme_pubr()
```

```{r estimate_summary_t}

format_estimate <- function(mean, quantiles) {
  m  <- str_pad(round(mean, 2), 4,  "right", 0)
  ll <- str_pad(round(quantiles[[1]], 2), 4,  "right", 0)
  ul <- str_pad(round(quantiles[[2]], 2), 4,  "right", 0)
  
  str_glue("{m} [{ll}-{ul}]")
}
tidy_pars_df %>% group_by(order, name) %>% 
  summarise(estimate = format_estimate(mean(value), 
                                       quantile(value, c(0.025, 0.975)))) %>% 
  pivot_wider(names_from = name, values_from = estimate) %>% 
  select(order, R_0, zeta, P_0, nu, upsilon)-> summary_est

colnames(summary_est) <- c("Order", "R(0)", "$\\zeta$", "P(0)", "$\\nu$", "$\\upsilon$")

knitr::kable(summary_est, "latex", booktabs = TRUE, escape = FALSE)
```

\newpage

# Prediction of hidden states

Based on the results above, we select the structure of order 5 as the model for
predicting hidden states.

```{r}
inc_df <- sim_incidences_list[[5]] %>% select(-order, -variable)

wkl_inc <- irish_data %>% slice(1:77)%>%
  mutate(week = ((time - 1) %/% 7) + 1) %>% 
  group_by(week) %>% summarise(y = sum(y)) %>% 
  mutate(time = week * 7)

wkl_df <- inc_df %>% filter(time <= 77) %>% 
  mutate(week = ((time - 1) %/% 7) + 1) %>% 
  group_by(iter, week) %>% 
  summarise(value = sum(value))

qs <- c(0.025, 0.25, 0.5, 0.75, 0.975)

pred_inc <- wkl_df %>% group_by(week) %>% 
  summarise(median = median(value), vals = quantile(value, qs),
            lims = c("q2.5", "q25", "q50", "q75", "q97.5")) %>% 
  pivot_wider(names_from = lims, values_from = vals)

g1 <- plot_wkl_fit(pred_inc, wkl_inc, "C[t]^w", "Incidence fit", 
                   shape = 18, STH_colour)
```

```{r}
actual_mob <- drv_data_obj$df %>% 
  mutate(week = time / 7) %>% 
  rename(y = y2)

mob_df <- Z_list[[5]] %>% select(-stock) %>% 
  mutate(week = time / 7)

qs <- c(0.025, 0.25, 0.5, 0.75, 0.975)

summary_mob <- mob_df %>% group_by(week) %>% 
  summarise(median = median(value), vals = quantile(value, qs),
            lims = c("q2.5", "q25", "q50", "q75", "q97.5")) %>% 
  pivot_wider(names_from = lims, values_from = vals)

g2 <- plot_wkl_fit(summary_mob, actual_mob, "Z[t]", "Mobility fit", 
                   18, STH_colour)
```

```{r}
source("./R_scripts/R_estimates.R")
pst_df <- posterior_list[[4]]

zeta_df <- pst_df %>% select(zeta) %>% 
  mutate(iter = row_number())

mob_df %>% rename(Z = value) %>% left_join(zeta_df, by = "iter") %>% 
  mutate(beta = zeta * Z,
         R    = estimate_r(beta)) -> R_df

R_df %>% mutate(week = time / 7) %>% 
  group_by(week) %>% 
    summarise(q50 = median(R), vals = quantile(R, c(0.025, 0.975)),
            lims = c("q2.5", "q97.5")) %>% 
  pivot_wider(names_from = lims, values_from = vals) -> summary_R

ggplot(summary_R, aes(x = week, y = q50)) +
  geom_line(colour = "steelblue") +
  geom_ribbon(alpha = 0.25, aes(ymin = q2.5, ymax = q97.5),
              fill = "steelblue") +
  labs(y = parse(text = "R[t]"), x = "Week",
       title = "Basic reproductive number")+
  scale_x_continuous(breaks = 1:11) +
  theme_pubr() +
  theme(axis.title = element_text(size = 8, colour = "grey40"),
        axis.text  = element_text(colour = "grey60", size = 6),
        plot.title = element_text(size = 9, colour = "grey25"),
        axis.ticks = element_line(colour = "grey60")) -> g3
```

```{r}
S_df %>% mutate(s = value / 4937796) -> s_df

bind_cols(R_df[, c("iter", "week", "R")], select(s_df, s)) %>% 
  mutate(Re = R * s) -> Re_df

summary_Re <- Re_df %>% group_by(week) %>% 
    summarise(q50 = median(R), vals = quantile(R, c(0.025, 0.975)),
            lims = c("q2.5", "q97.5")) %>% 
  pivot_wider(names_from = lims, values_from = vals)


ggplot(summary_Re, aes(x = week, y = q50)) +
  geom_hline(yintercept = 1, colour = "grey60", linetype = "dashed") +
  geom_line(colour = "steelblue") +
  geom_ribbon(alpha = 0.25, aes(ymin = q2.5, ymax = q97.5),
              fill = "steelblue") +
  geom_vline(xintercept = 1.86, colour = "grey50", linetype = "dotted") +
  annotate("text", x = 1.96, y = 6, size = 1.5,
             label = "Delay phase", hjust = 0, size = 3, colour = "grey50") +
  geom_vline(xintercept = 4, colour = "grey50", linetype = "dotted") +
  annotate("text", x = 4.1, y = 6, size = 1.5,
             label = "Stay at home", hjust = 0, size = 3, colour = "grey50") +
  labs(y = parse(text = "Re[t]"), x = "Week",
       title = "Effective reproductive number")+
  scale_x_continuous(breaks = 1:11) +
  theme_pubr()  +
  theme(axis.title = element_text(size = 8, colour = "grey40"),
        axis.text  = element_text(colour = "grey60", size = 6),
        plot.title = element_text(size = 9, colour = "grey25"),
        axis.ticks = element_line(colour = "grey60"))-> g4
```

```{r}
(g1 / g2) | (g3 / g4)
```



```{r}

tidy_pars_df %>% filter(order == 5) %>% select(-order) %>% 
  group_by(name) %>% summarise(mean   = mean(value), 
                               vals   = quantile(value, c(0.025, 0.975)),
                               lims   = c("lower_limit", "upper_limit")) %>% 
  pivot_wider(names_from = lims, values_from = vals) -> est_df


results_list <- list(label         = "M3 (SM4)",
                     sim_inc       = pred_inc,
                     sim_mob       = summary_mob,
                     R_t           = summary_R,
                     Re_t          = summary_Re,
                     estimates_df  = est_df)

fn <- file.path(folder, "predictions.rds")

if(!file.exists(fn)) saveRDS(results_list, fn)
```

