---
title: "GBM_immi"
author: "Jair Andrade"
date: "7/5/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE,
                      warning = FALSE)

library(doParallel)
library(doRNG)
library(dplyr)
library(imputeTS)
library(lubridate)
library(pomp)
library(purrr)
library(readr)
library(readxl)
library(stringr)
library(tictoc)
library(tidyr)

source("./R_scripts/plots.R")
```

# Data

## Incidence data

```{r}
source("./R_scripts/irish_data.R")

irish_data   <- get_irish_data()
total_cases  <- sum(irish_data$y)
formatted_tc <- format(total_cases, big.mark = ",")

wkl_inc <- irish_data %>% slice(1:77)%>%
  mutate(week = ((time - 1) %/% 7) + 1) %>% 
  group_by(week) %>% summarise(y = sum(y)) %>% 
  mutate(time = week * 7)
```

```{r}
source("./R_scripts/plots.R")
incidence_graphs(irish_data, formatted_tc, wkl_inc)
```


## Apple mobility

```{r}
source("./R_scripts/apple.R")

drv_data_obj <- get_driving_data()
imp <- drv_data_obj$imputed_data

wkl_df <- wkl_inc %>% rename(y1 = y) %>% 
  mutate(y2 = imp[1:length(imp) %% 7 == 0])
```

```{r, fig.height = 3.5}
driving_missing_data(drv_data_obj$raw_data)
```

```{r, fig.height= 3.5}
imputed_driving_data(drv_data_obj$raw_data,
                     drv_data_obj$imputed_data)
```

\newpage

# Geometric Brownian Motion (GBM) 

```{r}
#===============================================================================
# Model setup
#===============================================================================
folder <- "./Saved_objects/Irish_data/SEI3R_GBM/mdl_3" # includes immigration
source("./R_scripts/POMP_models.R")

par_obj      <- get_params("GBM_3")
params       <- par_obj$all
fixed_params <- par_obj$fixed
pomp_mdl     <- pomp_SEI3R_GBM_immi(wkl_df, params, 1 / 128)
```

## Likelihood variance test

```{r, GBM_3_test_lik_var}
source("./R_scripts/likelihood_funs.R")
source("./R_scripts/helpers.R")

fn <- file.path(folder, "pf_sensitivity.rds") # particle filter sensitivity
n_particles  <- c(5e3, 1e4, 2e4, 5e4, 1e5, 2e5, 5e5, 1e6)
sens_results <- pf_sensitivity(n_particles = n_particles, n_cores = 7, 
                               seed = 904296127, pomp_mdl = pomp_mdl, fn = fn,
                               n_iter = 14)
```

```{r, fig.height = 3}
source("./R_scripts/plots.R")
loglik_se_sens(sens_results)
```

## Inference

### Local search (Single guess)

\hfill

By applying iterated filtering, we search for maximum likelihood estimates from
a single guess for each unknown parameter. We repeat this process
**twenty** times.

```{r}
source("./R_scripts/local_search.R")
ptb    <- rw.sd(P_0 = ivp(0.02), tau = 0.02, zeta = 0.02, alpha = 0.02,
                iota = 0.02)
fn     <- file.path(folder, "local_search.rds")
ls_obj <- local_search(pomp_mdl, params, ptb, fn, 835816535, 7)
```

```{r}
mifs_local <- ls_obj$result

mifs_local %>%
  traces() %>%
  melt() -> traces_df 

mif_traces(traces_df, names(par_obj$unknown))
```

```{r, fig.height = 3}
loglik_traces(traces_df, c(-200, 0))
```

#### Likelihood

\hfill

To the parameter estimates found in the previous local search, we estimate their likelihood via particle filtering.

```{r}
source("./R_scripts/likelihood_funs.R")
fn <- file.path(folder, "local_search_ll.rds")

ll_local_search_obj <- mif_ll(mifs_local, seed = 627943112, n_cores = 7,
                              filename = fn)
```

```{r, message = TRUE}
source("./R_scripts/helpers.R")

ls_loglik_df <- extract_ll_df(ll_local_search_obj) %>% 
  filter(loglik > max(loglik) - 100) %>% 
  filter(loglik.se < 1)


pairs(~loglik+zeta + P_0 + alpha + tau + iota,
      data = ls_loglik_df, pch=16)
```

### Global search by iterated filtering

\hfill

```{r, message = FALSE}
mf1          <- ls_obj$result[[1]] 
fixed_params <- par_obj$fixed      

set.seed(87629711)

runif_design(
  lower = c(zeta = 0.1, P_0 = 1,  tau = 0.05, alpha = 0.05, iota = 0),
  upper = c(zeta = 3,   P_0 = 30, tau = 3, alpha = 0.3, iota = 10),
  nseq  = 300
) -> guesses

fn     <- file.path(folder, "Global_search.rds")
seed   <- 19631106
source("./R_scripts/global_search.R")
gs_obj <- global_search(guesses, fixed_params, mf1, fn, seed, 7)
```

```{r, message = FALSE}
mifs_global <- extract_mif_results(gs_obj)

mifs_global %>% 
  traces() %>%
  melt() -> traces_df 

mif_traces(traces_df, names(par_obj$unknown))
```

```{r, fig.height = 3}
source("./R_scripts/plots.R")
loglik_traces(traces_df, c(-200, 0))
```

#### Likelihood

\hfill

To the parameter estimates found in the previous **global search**, we estimate their likelihood via particle filtering.

```{r}
source("./R_scripts/likelihood_funs.R")
fn          <- file.path(folder, "Global_search_ll.rds" )
ll_obj      <- mif_ll(mifs_global, Np = 100000, 920499408, 
                      n_cores = 7, fn)
```

```{r, message = FALSE, fig.height = 4.5, fig.width = 6, fig.align = 'center'}
source("./R_scripts/helpers.R")

loglik_df <- extract_ll_df(ll_obj)

loglik_df %>% 
  filter(loglik > max(loglik)- 20, loglik.se < 2) %>%
  bind_rows(guesses) %>%
  mutate(type=if_else(is.na(loglik),"guess","result")) %>%
  arrange(type) -> guess_result_df

pairs(~loglik + zeta + P_0 + tau + alpha + iota, data = guess_result_df,
      col=ifelse(guess_result_df$type == "guess", grey(0.5),"red"),pch = 16,
      cex = 0.5,
      labels =c("Log lik", expression(zeta), "P_0", expression(tau),
                expression(alpha), expression(iota)))
```

### Profiles

To estimate confidence intervals, we employ the profile likelihood method.

```{r}
profile_list_GBM        <- vector(mode = "list", 
                                  length = length(par_obj$unknown))

unk_names               <- names(par_obj$unknown)
names(profile_list_GBM) <- unk_names 

unadjusted_profile_list <- profile_list_GBM
mcap_list               <- profile_list_GBM
```

\newpage

#### $\zeta$

\hfill

```{r GBM_zeta}
#===============================================================================
var_name <- "zeta"
#===============================================================================
```

```{r}
raw_likelihood(guess_result_df, var_name)
```

##### Starting points

\hfill


```{r, fig.height = 4, fig.width = 4.5, fig.align = 'center'}
loglik_df %>% 
  filter(loglik > max(loglik)- 20, loglik.se < 2) %>%
  sapply(range) -> box

set.seed(167826283)

other_pars <- unk_names[unk_names != var_name]

profile_design(
  zeta  = seq(0.4, 2,length = 50),
  lower = box[1, other_pars],
  upper = box[2, other_pars],
  nprof = 30, type = "sobol"
) -> guesses
```

```{r}
plot_guesses(guesses)
```

##### Profile traces

\hfill

```{r}
source("./R_scripts/likelihood_funs.R")
zeta_ptb <- rw.sd(P_0 = ivp(0.02), tau = 0.02, alpha = 0.02, iota = 0.02)

fn_ifp     <- file.path(folder, "ifp_zeta.rds" )

ifp_obj <- iter_filt_profile(mf1 = mf1, 
                             guesses = guesses,
                             fixed_params = fixed_params,
                             perturbations = zeta_ptb,
                             filename = fn_ifp,
                             seed = 105449832)
```